### 2021-06-11 paper/report.tex
New figures. Working on sizes.

So why is rapid testing so effective? In order to shed more light on this question,
Figure~\ref{fig:2021_scenarios_decomposition_tests} decomposes the difference in the
scenario without rapid tests only (purple line in
Figure~\ref{fig:2021_scenarios_newly_infected}) and the main specification into the three
channels for rapid tests. Tests for pupils have the smallest effect, which is largely
explained by the relatively small number of students (Only 18\% of our population are in
the education sector (pupils, teachers etc.) versus  46\% are workers outside the
education sector) and the fact that schools did not operate at full capacity during our
period of study. Almost 40\% come from tests at the workplace. Despite the fact that rapid tests for private reasons are phased in only late, they make up for more than
half of the total effect.\comment[id=HM]{How many tests are actually performed along each of the three dimensions? Could this be a quantity story rather than the directed testing story I am making up here as wishful thinking?}\comment[id=K]{This is only calculated very deeply inside the model. I'll try to save it.}

>>>>

So why is rapid testing so effective? In order to shed more light on this question,
Figure~\ref{fig:2021_scenarios_decomposition_tests} decomposes the difference in the
scenario without rapid tests only (purple line in
Figure~\ref{fig:2021_scenarios_newly_infected}) and the main specification into the three
channels for rapid tests. Tests for pupils have the smallest effect, which is largely
explained by the relatively small number of students (Only 18\% of our population are in
the education sector (pupils, teachers etc.) versus  46\% are workers outside the
education sector) and the fact that schools did not operate at full capacity during our
period of study. Almost 40\% come from tests at the workplace. Despite the fact that rapid tests for private reasons are phased in only late, they make up for more than
half of the total effect.\comment[id=HM]{How many tests are actually performed along each of the three dimensions? Could this be a quantity story rather than the directed testing story I am making up here as wishful thinking?}\comment[id=K]{Working on it.}
